### 2023-09-12 3.Design/crossbar.tex
Done for now, missing figures and a few TODOs

\section{Crossbar circuit}
\label{sec:xbarCircuit}

@@

That leads to the conclusion that the best thing to do is use a both serialized and parallel system, using the limiting inference time for our system to set the maximum serial size.

%TODO understand better \subsection{Sneak path problem}
\subsection{Usage}
Since the analog system is only simulated in the inference phase of the \ac{NN}, the resistance doesn't need to change during this phase. The weights only change during the training phase, and the resistances are just a rendition of the weights (section TODO : ref weigths to res)

>>>>

\section{Voltage-driven crossbar circuit}
\label{sec:xbarCircuit}

@@

That leads to the conclusion that the best thing to do is use a both serialized and parallel system, using the limiting inference time for our system to set the maximum serial size. Depending on the system we're using this circuit for, we might have different time requirements.

%TODO understand better \subsection{Sneak path problem}
\subsection{Symbol}
This is the symbol defined for the voltage based memristor crossbar array used in this thesis for a better undertsanding of the future circuits. It depends on several parameters, the number of inputs ($n_i$), the number of outputs ($n_o$) and the serial size ($n_s$).

%TODO : include figure

The total onChip area for the crossbar circuit depends on the previously defined parameters.

\begin{equation}
  A_{xbar}(n_i,n_o,n_s)=2\cdot n_i\cdot n_o \cdot n_s\cdot A_{memristor}+2\cdot A_{CMOS}\cdot n_o\cdot n_s +n_o\cdot(2\cdot[A_{opAmp}+A_R]+A_{R_f})
\end{equation}

With $A_{CMOS}$ being the same than for the memory cell (\cref{sec:memcell}), $A_{CMOS}=1.2\cdot 10^{-14}m^2$, and the feature size of typical memristor that can be fabricated at INESC is $2\mu m$, which would make the approximate area for a memristor $A_{memristor}=4\mu m^2=4\cdot 10^{-12} m^2$.%TODO check info and inesc citation

\subsection{Usage}

TODO Show off results

The analog system is only simulated in the inference phase of the \ac{NN}. And since the weights only change during the training phase, and the resistances are just a rendition of the weights (TODO : ref weigths to res), the resistances don't need to change, the circuit used in the simulations is thus using resistors instead of memristors for the sake of simplicity (notably in generating the netlist of the system, TODO ref how hard it is to import parameters using spice netlists).
